Tables

### 2019-12-13 manuscript/tables.Rmd
adjustment to DAI LIME results table

DAI_lime_analysis_table %>%
  kable(format = 'latex',booktabs = TRUE,escape = FALSE,caption = ' ') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

>>>>

DAI_lime_analysis_table %>%
  kable(format = 'latex',booktabs = TRUE,escape = FALSE,caption = ' ') %>%
  collapse_rows(columns = 1:4, latex_hline = "custom", valign = "middle",custom_latex_hline = 1:4)
```
